\documentclass[11pt]{meetingmins} % Using meetingmins LaTeX class.

\setcommittee{Project Group: Machine Learning for Predictive Maintenance}

\setdate{August 12, 2021. 10:00 - 11:00}

\setpresent{Tanja Tornede \textit{(Supervisor)}, Christopher Zinda, Paul Fährmann, Sanjay Gupta, Vinay Kaundinya.}

\absent{}

\begin{document}

\maketitle

\section{Minutes-taker: Sanjay Gupta}

\section{Topics Discussed:}

\subsection{Implementation}
\subsubsection{Details}
\begin{hiddensubitems}
    \item @Paul, refer research paper to understand how cmapss dataset is build and works.
    \item @Paul, emit constant timeseries and then add to Pipeline elements.
    \item @Paul, do absolute cut not percentage cut for cmapss dataset splits.
    \item Decided on possible final project presentation date ( 15.09.2021, 22.09.2021, 29.09.2021).
    \item Next week we will discuss about what will be there in presentation.
    \item Complete or fix the your code in GitLab by Wednesday after that it will be closed (No more commits). Until it's major issue or changes commits will not be allowed.
    \item Test your code completely with other test combinations until Wednesday.
    \item Maybe after completion of project GitLab repository. It will move to Github (by @Tanja).
    \item Brainstorm the pattern or structure for final project presentation.
    \item Add getting started and readme file in GitLab project repository.
\end{hiddensubitems}

\section{Next Meeting:}
\begin{hiddensubitems}
    \item Date and time: August 19, 2021 at 13:30 - 15:30
    \item Person responsible for minutes: Vinay Kaundinya
\end{hiddensubitems}
\end{document}
