\documentclass[11pt]{meetingmins} % Using meetingmins LaTeX class.

\setcommittee{Project Group: Machine Learning for Predictive Maintenance}

\setdate{July 08, 2021. 10:00 - 11:00}

\setpresent{Tanja Tornede\textit{(Supervisor)}, Paul Fährmann, Sanjay Gupta, Vinay Kaundinya.}

\absent{Christopher Zinda}

\begin{document}

\maketitle

\section{Minutes-taker: Paul Fährmann}

\section{Topics Discussed:}

\subsection{Implementation}
\subsubsection{Details}
\begin{hiddensubitems}
    \item Discussed the EMD-Signal wrapper and how to handle different output lengths of the instances. Further discussion after a better explanation and visualization on these imf components in the general chat.
    \item Discussed test coverage strategy for the tsfresh wrapper class. Don't test individual output values, just execute the code and check simple shapes of output and check error outputs.
    \item Should extract example/mock data into higher folder for tests, so everyone can use it in their tests.
    \item If your approach does not generate the same quality/result as a paper, it could just be a difference in the random seed used in the approach.
    \item Can we use different architectures for neural networks for the approaches? Yes, could be interesting, especially if there is also paper about it.
    \item Windowed predictor is still in the room, we will discuss about it next week, when Christopher is available.
\end{hiddensubitems}

\section{Next Meeting:}
\begin{hiddensubitems}
    \item Date and time: July 15, 2021 at 10:00 - 12:00
    \item Person responsible for minutes: Sanjay Gupta
\end{hiddensubitems}
\end{document}
