\documentclass[11pt]{meetingmins} % Using meetingmins LaTeX class.

\setcommittee{Project Group: Machine Learning for Predictive Maintenance}

\setdate{August 19, 2021. 13:30 - 15:30}

\setpresent{Tanja Tornede \textit{(Supervisor)}, Christopher Zinda, Paul Fährmann, Sanjay Gupta, Vinay Kaundinya.}

\absent{}

\begin{document}

\maketitle

\section{Minutes-taker: Vinay Kaundinya}

\section{Topics Discussed:}

\subsection{Implementation}
\subsubsection{Details}
\begin{hiddensubitems}
    \item Discussed progress for the week W32.
    \item @Paul discussed about the attribute filter that is newly added, in context of timeseries processing and constant sensor value columns.
    \item @Paul, currently working on multi processing of timeseries, parallelization ideas etc with sklearn (njobs). Have a method for attribute filter (in dataset class) or as a pipeline element.
    \item @Sanjay RNN encoder, Weighted Avg already implemented and merged to Develop and windowing approach (already implemented by Christopher).
    \item @Vinay to merge SVR, CNN and LSTM approaches to develop.
    \item @Christopher to implement and finalize Random forest approach.
    \item Discussed about having a verbose like parameter for ml4pdm(every?) pipeline element. @Sanjay
    \item Discussed initial details of documentation(sphinx) and final presentation.
\end{hiddensubitems}

\section{Next Meeting:}
\begin{hiddensubitems}
    \item Date and time: August 26, 2021 at 10:00 - 12:00
    \item Person responsible for minutes: Christopher Zinda
\end{hiddensubitems}
\end{document}
