\documentclass[11pt]{meetingmins} % Using meetingmins LaTeX class.

\setcommittee{Project Group: Machine Learning for Predictive Maintenance}

\setdate{September 9, 2021. 13:00 - 14:00}

\setpresent{Tanja Tornede \textit{(Supervisor)}, Christopher Zinda, Paul Fährmann, Sanjay Gupta, Vinay Kaundinya.}

\absent{}

\begin{document}

\maketitle

\section{Minutes-taker: Sanjay Gupta}

\section{Topics Discussed:}

\subsection{Final phase}
\subsubsection{Details}
\begin{hiddensubitems}
    \item @Team finalized the logo design (Applause to @Vinay) for the ML4PdM library with @Tanja.
    \item @Christopher, Updated the readme file contents, introduction and installation process in documentation and GitLab repository.
    \item Add @Tanja email-id and description for future contact person.
    \item @Team, check correct copyright and licenses for the library to register.
    \item Check all libraries we are using in our project and find out which licenses are needed for ML4PdM library.
    \item Cross verify all changelogs are correctly mentioned in documentation and GitLab repository.
    \item Put ML4PdM library logo somewhere on each slide in PPT.
    \item The planned contents structure for presentation is very poor. @Team needed to planned better structure.
    \item @Tanja, gave small demo on what we can include in presentation. No need to explain all the approaches. Create flowchart of the pipelines and give demo on that.
    \item @Tanja, suggested to give demo of pipelines workflow and installation process in presentation.
    \item After motivation, @Team can add how to create configuration file in presentation.
    \item Add different ways to run the library in presentation. example- with or/and without configuration file.
    \item @Tanja, suggested to follow the following structure for presentation: Motivation, flowchart with examples, How to use the library.
\end{hiddensubitems}

\section{Next Meeting:}
\begin{hiddensubitems}
    \item Date and time: September 16, 2021 at 10:00 - 12:00
    \item Person responsible for minutes: Vinay Kaundinya
\end{hiddensubitems}
\end{document}
