\documentclass[11pt]{meetingmins} % Using meetingmins LaTeX class.

\setcommittee{Project Group: Machine Learning for Predictive Maintenance}

\setdate{July 29, 2021. 10:30 - 12:50}

\setpresent{Tanja Tornede\textit{(Supervisor)}, Christopher Zinda, Paul Fährmann, Sanjay Gupta, Vinay Kaundinya.}

\absent{}

\begin{document}

\maketitle

\section{Minutes-taker: Vinay Kaundinya}

\section{Topics Discussed:}

\subsection{Implementation}
\subsubsection{Details}
\begin{hiddensubitems}
    \item Discussed dataset extension details, methods to transform TS data to list and strings to attribute types using attribute classes. Additions: Individual parse functions.
    \item Discussed Sanjay's progress on TS fresh wrapper implementation(fixing code smells), rnn autoencoder review.
    \item Improve tsfresh constructor implementation. Default parameters 'False', example: get set of active parameters, set contains element from enum, anything that is not in set deactivate.
    \item Discussed asymmetric loss numbers and RMSE values for Direct RUL, CNN and LSTM approach. Additions: adapt to windowed predictor approach.
    \item Discussed multiple classifier approach, RMSE and MSE values are as expected but not asymmetric score. Christopher to work on windowed predictor.
    \item Discussed plan for week 31.
    \item Discussed timeseries to numpy(and vice versa) transformation functions. Only timeseries stuff to list or numpy was discussed earlier and not transformation of all features.
    \item Discussed to have a wrapper function for scalers.
\end{hiddensubitems}

\section{Next Meeting:}
\begin{hiddensubitems}
    \item Date and time: August 05, 2021 at 10:00 - 12:00
    \item Person responsible for minutes: Paul Fährmann
\end{hiddensubitems}
\end{document}
